---
title: "homework4"
author: "Ruyue Zhang"
date: "11/6/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## introduction of this investigation
I've always been intrested in skin-care and followed many bloggers who introduce their skin care preference and routine on youtube. But I alwayse have these doubt, and I believe many people do, such as would make-up products do harm to our skin? And whether sun-care products would keep skin in a better condition? 

Based on these I designed a survey using Google form and put the link on my Facebook and also Friends Circle (the most popular platform in China). 

## web link of this survey
https://goo.gl/forms/zJyiOKESUtL4oErg2

## read in data
```{r}
setwd("~/desktop/STATISTICAL COMPUTING/homework4")
skincare<-read.table("Skin-Care.csv",head=TRUE,sep=",")
skincare<-skincare[,-1]
colnames(skincare)<-c("gender","age","income","skincare-frequency","money spent","skin-type","numberofproducts_day", "makeup_frequency","aspect","suncare_frequency","condition","age_start","time_skincare_day")
##recode some variables as numerical for later use
##gender female=1 male=2 other=0
skincare[,1]<-gsub('female',1,skincare[,1],fixed=TRUE)
skincare[,1]<-gsub('male',2,skincare[,1],fixed=TRUE)
skincare[,1]<-gsub('other',0,skincare[,1],fixed=TRUE)
skincare[,1]<-as.numeric(skincare[,1])
##age <20=1 20s=2 30s=3 40s=4 above 50=5
skincare[,2]<-gsub('below 20',1,skincare[,2],fixed=TRUE)
skincare[,2]<-gsub('20s',2,skincare[,2],fixed=TRUE)
skincare[,2]<-gsub('30s',3,skincare[,2],fixed=TRUE)
skincare[,2]<-gsub('40s',4,skincare[,2],fixed=TRUE)
skincare[,2]<-gsub('above 50',5,skincare[,2],fixed=TRUE)
skincare[,2]<-as.numeric(skincare[,2])
##skin-type oily=1 dry=2 sensitive=3 combinational=4 normal=5
skincare[,6]<-gsub('combinational',4,skincare[,6],fixed=TRUE)
skincare[,6]<-gsub('oily',1,skincare[,6],fixed=TRUE)
skincare[,6]<-gsub('dry',2,skincare[,6],fixed=TRUE)
skincare[,6]<-gsub('sensitive',3,skincare[,6],fixed=TRUE)
skincare[,6]<-gsub('normal',5,skincare[,6],fixed=TRUE)
skincare[,6]<-as.numeric(skincare[,6])
##skin-care frequency never=1 every day=2 occasionally=3
skincare[,4]<-gsub('never',1,skincare[,4],fixed=TRUE)
skincare[,4]<-gsub('every day',2,skincare[,4],fixed=TRUE)
skincare[,4]<-gsub('occasionally',3,skincare[,4],fixed=TRUE)
skincare[,4]<-as.numeric(skincare[,4])
##sun-care preference every day=2 sunny=1 never=0
skincare[,10]<-gsub('every day',2,skincare[,10],fixed=TRUE)
skincare[,10]<-gsub('only when it is sunny',1,skincare[,10],fixed=TRUE)
skincare[,10]<-gsub('never',0,skincare[,10],fixed=TRUE)
skincare[,10]<-as.numeric(skincare[,10])
##skin condition below average=0 average=1 good=2 perfect=3
skincare[,11]<-gsub('below average',0,skincare[,11],fixed=TRUE)
skincare[,11]<-gsub('average',1,skincare[,11],fixed=TRUE)
skincare[,11]<-gsub('good',2,skincare[,11],fixed=TRUE)
skincare[,11]<-gsub('perfect',3,skincare[,11],fixed=TRUE)
skincare[,11]<-as.numeric(skincare[,11])
##number of products for one day
skincare[,7]<-as.numeric(skincare[,7])
##get a histogram of number of skin-care products for one day
hist(skincare[,7],xlab='products for one day',main='histogram of skin-care products for one day')
box()
##use t-test to decide if there is a relationship between gender and skin-type
t.test(skincare[,1],skincare[,6],conf.level=0.95)
##use t-test to decide if there is a relationship between age and skin-type
t.test(skincare[,2],skincare[,6])
##decide whether using sun-care products will actually affect skin condition
t.test(skincare[,10],skincare[,11])
##add
```

